### 2024-07-18 evaluating-prediction-accuracy.qmd
20240717 - package bibliography

There are two primary dimensions of accuracy: (1) [discrimination](#sec-discrimination) and (2) [calibration](#sec-calibration).
Some general indexes of accuracy combine discrimination and calibration, as described in @sec-generalAccurac.
In addition, accuracy indices can be [threshold-dependent](#sec-thresholdDependentAccuracy) or [-independent](#sec-thresholdIndependentAccuracy) and can be scale-dependent or -independent.
[Threshold-dependent accuracy indices](#sec-thresholdDependentAccuracy) differ based on the cutoff (i.e., threshold), whereas [threshold-independent accuracy indices](#sec-thresholdIndependentAccuracy) do not.
Thus, raising or lowering the cutoff will change [threshold-dependent](#sec-thresholdDependentAccuracy) accuracy indices.
Scale-dependent accuracy indices depend on the metric/scale of the data, whereas scale-independent accuracy indices do not.
Thus, scale-dependent accuracy indices cannot be directly compared when using measures of differing scales, whereas scale-independent accuracy indices can be compared across data of differing scales.

@@

@@

Test bias refers to systematic error (in measurement, prediction, etc.) as a function of group membership that leads the same score to have different meaning for different groups.
For instance, if the Wonderlic Contemporary Cognitive Ability Test is a strong predictor of performance for Quarterbacks but not for Running Backs, the test is biased.
Test bias, including how to identify and address it, is described in [Petersen (2024)](https://isaactpetersen.github.io/Principles-Psychological-Assessment/bias.html).

>>>>

There are two primary dimensions of accuracy: (1) [discrimination](#sec-discrimination) and (2) [calibration](#sec-calibration).
Some general indexes of accuracy combine discrimination and calibration, as described in @sec-generalAccuracy.
In addition, accuracy indices can be [threshold-dependent](#sec-thresholdDependentAccuracy) or [-independent](#sec-thresholdIndependentAccuracy) and can be scale-dependent or -independent.
[Threshold-dependent accuracy indices](#sec-thresholdDependentAccuracy) differ based on the cutoff (i.e., threshold), whereas [threshold-independent accuracy indices](#sec-thresholdIndependentAccuracy) do not.
Thus, raising or lowering the cutoff will change [threshold-dependent](#sec-thresholdDependentAccuracy) accuracy indices.
Scale-dependent accuracy indices depend on the metric/scale of the data, whereas scale-independent accuracy indices do not.
Thus, scale-dependent accuracy indices cannot be directly compared when using measures of differing scales, whereas scale-independent accuracy indices can be compared across data of differing scales.

@@

$$
\begin{aligned}
  \text{mean error} &= \frac{\sum\limits_{i = 1}^n(\text{predicted}_i - \text{observed}_i)}{n} \\
  &= \text{mean}(e_i)
\end{aligned}
$$ {#eq-meanError}

@@

Test bias refers to systematic error (in measurement, prediction, etc.) as a function of group membership that leads the same score to have different meaning for different groups.
For instance, if the Wonderlic Contemporary Cognitive Ability Test is a strong predictor of performance for Quarterbacks but not for Running Backs, the test is biased.
Test bias, including how to identify and address it, is described in [@PetersenPrinciplesPsychAssessment](https://isaactpetersen.github.io/Principles-Psychological-Assessment/bias.html).

### 2024-07-18 index.qmd
20240717 - package bibliography

@@

In terms of my `R` and statistics background, I have published many [peer-reviewed publications](https://developmental-psychopathology.lab.uiowa.edu/publications) that employ advanced statistical methods, have published a [book on psychological assessment](https://www.routledge.com/9781032413068) [@Petersen2024a; @PetersenPrinciplesPsychAssessment] that includes applied examples in `R`, and have published the [`petersenlab` `R` package](https://cran.r-project.org/web/packages/petersenlab/index.html) [@R-petersenlab] on the Comprehensive R Archive Network (CRAN).
Several sections in this book come from @PetersenPrinciplesPsychAssessment.
I am also a co-author of the [`ffanalytics` `R` package](https://github.com/FantasyFootballAnalytics/ffanalytics) that provides free utilities for downloading fantasy football projections and additional fantasy-relevant data, and for calculating projected points given your league settings.

>>>>

```{r}
#| include: false

# Automatically create a bib database for R packages
packagesForBibliography <- c(
  "petersenlab", "ffanalytics", "pROC", "rms"
)

knitr::write_bib(
  c(.packages(), packagesForBibliography),
  "packages_new.bib")
```

@@

In terms of my `R` and statistics background, I have published many [peer-reviewed publications](https://developmental-psychopathology.lab.uiowa.edu/publications) that employ advanced statistical methods, have published a [book on psychological assessment](https://www.routledge.com/9781032413068) [@Petersen2024a; @PetersenPrinciplesPsychAssessment] that includes applied examples in `R`, and have published the [`petersenlab` `R` package](https://cran.r-project.org/web/packages/petersenlab/index.html) [@R-petersenlab] on the Comprehensive R Archive Network (CRAN).
Several sections in this book come from @PetersenPrinciplesPsychAssessment.
I am also a co-author of the [`ffanalytics` `R` package](https://github.com/FantasyFootballAnalytics/ffanalytics) [@R-ffanalytics] that provides free utilities for downloading fantasy football projections and additional fantasy-relevant data, and for calculating projected points given your league settings.
